Supplementary Materials

### 2018-03-25 paper/task.tex
update task

%
%A stereotypical scenario can be summarized as the follow.
%
To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.

Look at example, perturb the example, see how the perturb the one fails,

learn the limitation and strength from the where and how the errors occurs. iterate

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{errorAnalysis}
 \caption{How domain experts conduct error analysis on the model.}
\label{fig:modelPipeline}
\end{figure}

\begin{itemize}
\item \textbf{G1} Understand how attention affect the prediction 
\item \textbf{G2} Why sentences are misclassified 
\item \textbf{G3} 
\item \textbf{G4} 
\end{itemize}

\begin{itemize}
\item \textbf{T1} Encode the internal state \emph{attention} of the model
\end{itemize}

>>>>

%
A stereotypical scenario can be summarized as the follow.
To assess a model for a specific NLP task, the research start the analysis by looking at the failure cases.
Look at example, perturb the example, see how the perturb the one fails,
learn the limitation and strength from the where and how the errors occurs. iterate

%\begin{figure}[htbp]
%\centering
%\vspace{-2mm}
% \includegraphics[width=1.0\linewidth]{errorAnalysis}
% \caption{How domain experts conduct error analysis on the model.}
%\label{fig:modelPipeline}
%\end{figure}

Analysis Goal
\begin{itemize}
\item \textbf{G1} Understand how attention affect the prediction 
\item \textbf{G2} Why sentences are misclassified 
\item \textbf{G3} 
\item \textbf{G4} 
\end{itemize}

Visualization Tasks
\begin{itemize}
\item \textbf{T1} Encode the internal state \emph{attention} of the model
\end{itemize}
